Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-23 Paper/ms.tex
Lookup table

\section{Orbit Simulations}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations is needed in order to evaluate the likelihood
function for any proposed setting of the parameters.
To save time, we pre-computed the properties of orbits as a function of
ellipticity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.

>>>>

\section{Orbit Look-Up Table}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations is needed in order to evaluate the likelihood
function for any proposed setting of the parameters.
To save time, we pre-computed the properties of orbits as a function of
ellipticity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.
